\documentclass[a4paper,11pt]{amsart}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\begin{document}
\thispagestyle{empty}
\ \\
{\bf Recommendation for Giulio Cerbai}\hfill 26 November 2020
\bigskip
\bigskip
\bigskip

I know Giulio quite well. We met at a conference in 2018 and we have
been working together on various projects since then. Giulio is
currently a PhD student at the University of Florence and he is expected
to graduate in the spring of 2021. I visited Florence to work with
Giulio and Luca Ferrari (Giulio's advisor) in late 2018. Giulio,
conversely, visited me at UI for a month in 2019.

I am currently working with Giulio on a couple of research projects. One
is about sorting algorithms and permutation patterns. The other is about
endo\-functions and so called transport theorems. Giulio is the driving
force of both projects. To be honest I have problems keeping up with
him.

As can be seen in Giulio's CV he has already 10 papers that are either
published in high quality international journals or have been submitted
to such journals, and I know that there are more papers under
preparation. This is deeply impressive for a researcher who is yet to
receive his PhD.

Another thing that has impressed me about Giulio is the speed with which
he has become an expert programmer. I am a keen programmer myself and I
have been programming since I was a teenager. I often reach for the
computer when testing a conjecture, but when working with Giulio I most
often don't have to, because Giulio has already done so.

Giulio's writing skills could be further improved.

In summary, my experience of interacting with Giulio could not be more
positive; he's curious, intelligent and a very mature and independent
worker for such an early stage in his career. He easily handles big work
loads; in fact, he seems to thrive under pressure.  Giulio would be a
fantastic addition to the University of Iceland. His application has my
unreserved and enthusiastic support.

\ \\
Yours sincerely,\smallskip\\
Professor Anders Claesson \\
University of Iceland
\end{document}
