\documentclass[a4paper,10pt]{amsart}

\begin{document}
\thispagestyle{empty}
\ \\
{\bf Recommendation for Jason P Smith}\hfill 22 November 2014
\bigskip
\bigskip
\bigskip

\noindent
I am Jason's second advisor. The topic of his PhD thesis is the M\"obius
function of the pattern poset. Since the seminal "Restricted
permutations" paper in a 1985, by Simion and Schmidt, problems
concerning permutations and their patterns (substructures) have received
a lot of attention in the Combinatorics community. One of the most
fundamental problems in this area is to understand the poset of
permutations under pattern containment, and in particular its M\"obius
function. \medskip

\noindent
This is, in general, an extremely hard problem. Jason has nevertheless
made significant progress: he has computed the M\"obius function and
established shellability of certain families of intervals in the
poset. This is highly original work and he has produced two papers
(without collaborators) on the topic, one of which has already been
published in The Electronic Journal of Combinatorics.  \medskip

\noindent
My experience of interacting with Jason could not be more positive.  He
has a modest, quiet and likable personality. Jason is an independent
worker, determined, intelligent and hard working. I believe he has a
bright future as a mathematician. Jason will no doubt make a lasting
mark on Combinatorics and his application for a Heilbronn Research
Fellowship has my complete and unqualified support. \medskip

% \noindent
% I was also asked to suggest addition assessors of the candidate's
% writings, and here is my short list: Dr Robert Brignall (The Open
% University); Prof Nik Ru\v{s}kuc (University of St Andrews); Prof Bruce
% Sagan (Michigan State University).

\ \\
Yours sincerely,\smallskip\\
Anders Claesson \\
Senior Lecturer \\
University of Strathclyde
\end{document}
